### 2017-07-06 manuscript/usses_water_ms.Rmd
adds outcomes figure
tries new title...

\Large{\textbf{Ecosystem and community resistance to five years of drought and deluge in a sagebrush steppe}}

@@

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{../figures/rank_clocks_scaled_abundance.png}
  \caption{Rank clocks of average species' scaled abundance by treatment. (A) All species. (B) Dominant species.}
\end{figure}

>>>>

\Large{\textbf{Consistent ecosystem functional response to soil moisture during five years of drought and deluge in a sagebrush steppe}}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=4in]{../figures/hypothesis_figtable.png}
  \caption{Possible outcomes of chronic resource alteration.}
\end{figure}

@@

<!---
\newpage{}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{../figures/rank_clocks_scaled_abundance.png}
  \caption{Rank clocks of average species' scaled abundance by treatment. (A) All species. (B) Dominant species.}
\end{figure}
---->
